% NeurIPS 2026 Paper Checklist (mandatory; does not count toward 9-page limit).
% Replace this stub with the official checklist.tex from the Overleaf
% template (bjdwqfdkyftc) before submission. Items are pre-filled with
% scPTR-specific answers; verify each "Justification" against the final
% manuscript text.

\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
  \item[] Question: Do the main claims made in the abstract and introduction
  accurately reflect the paper's contributions and scope?
  \item[] Answer: \answerYes{}
  \item[] Justification: Abstract and introduction enumerate the five
  contributions (per-cell $\gamma$ estimator, expression-invisible PT states,
  PT velocity, RBP network, DeepPTR) that map 1:1 to \Cref{sec:method,sec:results}.

\item {\bf Limitations}
  \item[] Question: Does the paper discuss the limitations of the work?
  \item[] Answer: \answerYes{}
  \item[] Justification: \Cref{sec:discussion} lists steady-state assumption
  failure, sparse-chemistry sensitivity, and confounding from library size.

\item {\bf Theory assumptions and proofs}
  \item[] Question: For each theoretical result, full set of assumptions and
  complete proof?
  \item[] Answer: \answerNA{}
  \item[] Justification: This is a Use-Inspired contribution; assumptions for
  the kinetic identity are stated where used (\Cref{sec:method}).

\item {\bf Experimental result reproducibility}
  \item[] Question: Information needed to reproduce main experimental results?
  \item[] Answer: \answerYes{}
  \item[] Justification: Code, fixed seeds, datasets via Pooch, and
  per-figure notebooks ship in the anonymized supplementary ZIP.

\item {\bf Open access to data and code}
  \item[] Question: Open access to data and code with sufficient instructions?
  \item[] Answer: \answerYes{}
  \item[] Justification: Anonymous code release in supplementary; public
  release planned upon acceptance under MIT license. Datasets are
  third-party, redistributed under their original licenses via Pooch.

\item {\bf Experimental setting/details}
  \item[] Question: Specify all training and test details?
  \item[] Answer: \answerYes{}
  \item[] Justification: Hyperparameters, seeds, optimiser, schedule in
  \Cref{app:deepptr}; analytic-estimator settings in \Cref{sec:method}.

\item {\bf Experiment statistical significance}
  \item[] Question: Statistical significance of experiments?
  \item[] Answer: \answerYes{}
  \item[] Justification: Spearman $\rho$ with $p$-values, miRNA enrichment
  $p$-values with FDR, zero-permutation controls, subsampling robustness
  reported in \Cref{sec:results-validation,sec:results-states}.

\item {\bf Experiments compute resources}
  \item[] Question: Compute resources for each experiment?
  \item[] Answer: \answerYes{}
  \item[] Justification: Single A100 for DeepPTR (12 min largest dataset);
  analytic pipeline scales sub-linearly to $10^5$ cells in $\sim$91\,s on a
  single CPU (\Cref{sec:results-validation,app:deepptr}).

\item {\bf Code of ethics}
  \item[] Question: Conform with the NeurIPS Code of Ethics?
  \item[] Answer: \answerYes{}
  \item[] Justification: Observational secondary analysis of public scRNA-seq;
  no human subjects work; no PII.

\item {\bf Broader impacts}
  \item[] Question: Discussion of potential positive and negative societal
  impacts?
  \item[] Answer: \answerYes{}
  \item[] Justification: \Cref{sec:discussion} addresses misuse risk and
  cautions against using inferred networks as standalone clinical targets.

\item {\bf Safeguards}
  \item[] Question: Safeguards for responsible release?
  \item[] Answer: \answerNA{}
  \item[] Justification: No high-risk artefacts (models, generative content,
  scraped datasets) are released.

\item {\bf Licenses for existing assets}
  \item[] Question: Original licenses cited?
  \item[] Answer: \answerYes{}
  \item[] Justification: scVelo, scanpy, AnnData (BSD); pancreas/dentate
  gyrus/A549 datasets retain their original licenses; sci-fate and
  neuroblastoma data are public.

\item {\bf New assets}
  \item[] Question: New assets well-documented?
  \item[] Answer: \answerYes{}
  \item[] Justification: scPTR is documented via README, API docstrings, and
  reproducibility notebooks in the supplementary.

\item {\bf Crowdsourcing and research with human subjects}
  \item[] Question: Disclosure of crowdsourcing or human-subjects work?
  \item[] Answer: \answerNA{}

\item {\bf IRB approvals or equivalent}
  \item[] Question: IRB approvals?
  \item[] Answer: \answerNA{}

\item {\bf Declaration of LLM usage}
  \item[] Question: Original LLM-usage declaration?
  \item[] Answer: \answerYes{}
  \item[] Justification: LLMs were used as a writing aid only (grammar,
  rephrasing), not as part of the methodology. No LLM-generated content
  is presented as an experimental result.

\end{enumerate}

% \answerYes / \answerNo / \answerNA / \answerTODO are provided by neurips_2026.sty.
